Title Text

### 2014-04-05 intromoa.tex
All notes in.
I hope you can read this today. I am  anxious to have your edits. Cut
or add anything you wish to make things clear.
I felt it would be easier to add all gory details and have you remove
as much as you can say in words during the talk. As mentioned I left
out many details.

Get shape: 
\begin{eqnarray}
\rho X & = & \rho (2 \take (\Phi A)) \nonumber \\
& = & 2 \cat ((1\drop (\rho ( \Phi A)))) \nonumber \\
&=& 2 \cat ((1 \drop (\rho  A))) \nonumber \\
&=& 2 \cat <\;5\;4> \nonumber \\
&=& <2\;4\;5>
\end{eqnarray}
Now that we have the {\em shape}, we can {Psi-Reduce}.
\[ \forall \;\;\; i,j,k \;\;\; \ni \;\;\; 0 \;\;\;\leq i,j,k < \;\;\;<2\;4\;5> \]
\[<i\;j\;k> \psi X \]
\begin{eqnarray}
& =&<i\;j\;k> \psi (2 \take ( \Phi A)) \times ( 1 \drop (\Phi A)) \nonumber \\
&=&<j\;k> \psi (<i> \psi (2 \take ( \Phi A)) \times ( 1 \drop (\Phi A)) )\nonumber \\
&= &<j\;k> \psi ((<i> \psi ( 2 \take (\Phi A))) \nonumber \\
&&\;\;\;\;\;\times ( <i> \psi ( 1 \drop (\Phi A)))) \nonumber \\
&= &<j\;k> \psi (( <i> \psi (\Phi A)) \times (<i+1> \psi (\Phi A))) \nonumber \\
&=&<j\;k> \psi ((<((\rho A)[0] - 1 - i)> \psi A ) \nonumber \\
&& \;\;\;\;\;\times  (<((\rho A)[0] - 1 -( i + 1))> \psi A ) )\nonumber \\
&=&<j\;k> \psi ((< 2-i> \psi A ) \times (<1-i>  \psi A) )
 \end{eqnarray}
\normalsize
This is the DNF, or semantic normal form. To proceed further we must know more about the data, i.e. layout, and architecture. 
\subsection{Applying the Psi Correspondence Theorem\cite{jen94}]
We now want to {\em transform} the DNF to a {\em Generic} Operational Normal Form (ONF) or way 
to {\em build the code}.

>>>>

Get shape: 
\begin{eqnarray}
\rho X & = & \rho (2 \take (\Phi A)) \nonumber \\
& = & 2 \cat ((1\drop (\rho ( \Phi A)))) \nonumber \\
&=& 2 \cat ((1 \drop (\rho  A))) \nonumber \\
&=& 2 \cat <\;5\;4> \nonumber \\
&=& <2\;4\;5>
\end{eqnarray}
Now that we have the {\em shape}, we can {Psi-Reduce}.
\[ \forall \;\;\; i,j,k \;\;\; \ni \;\;\; 0 \;\;\;\leq i,j,k < \;\;\;<2\;4\;5> \]
\[<i\;j\;k> \psi X \]
\begin{eqnarray}
& =&<i\;j\;k> \psi (2 \take ( \Phi A)) \times ( 1 \drop (\Phi A)) \nonumber \\
&=&<j\;k> \psi (<i> \psi (2 \take ( \Phi A)) \times ( 1 \drop (\Phi A)) )\nonumber \\
&= &<j\;k> \psi ((<i> \psi ( 2 \take (\Phi A))) \nonumber \\
&&\;\;\;\;\;\times ( <i> \psi ( 1 \drop (\Phi A)))) \nonumber \\
&= &<j\;k> \psi (( <i> \psi (\Phi A)) \times (<i+1> \psi (\Phi A))) \nonumber \\
&=&<j\;k> \psi ((<((\rho A)[0] - 1 - i)> \psi A ) \nonumber \\
&& \;\;\;\;\;\times  (<((\rho A)[0] - 1 -( i + 1))> \psi A ) )\nonumber \\
&=&<j\;k> \psi ((< 2-i> \psi A ) \times (<1-i>  \psi A) )
 \end{eqnarray}
\normalsize
This is the DNF, or semantic normal form. To proceed further we must know more about the data, i.e. layout, and architecture. 
\subsection* {Applying the Psi Correspondence Theorem: PCT}
We now want to {\em transform} the DNF above to a {\em Generic} Operational Normal Form (ONF) or way 
to {\em build the code}.  The PCT~\cite{muljen94} turns cartesian coordinates into start, stops, and strides.
Note that we still use {\em Psi-Reduction} but now just on vectors.  
Let Y denote $(<2-i> \psi A ) \times ( <1-i> \psi A)$. Then the shape of Y, i.e.
\begin{eqnarray}
\rho Y= 1 \drop (\rho A) = 1 \drop <3\;5\;4> = <5\;4>
\end{eqnarray}
i.e. the bounds for j and k  above.
Continuing with the PCT to create the {\em generic} ONF on p=2 processors, we use the index of the primary axis, i, $\ni\;\;0 \leq  i < p$, since $\rho X = <2\;4\;5>$.
Since we are accessing contiguous planes we can collapse j and k into a single index l, $\ni \;\; 0 \leq l <20$.
Using $\gamma_row$ for row major ordering, Y is transformed into:
\small
\begin{eqnarray}
a[ (( \gamma(<2-i >; <1 \take (\rho A>))) \times \pi ( 1 \drop (\rho A))   )  + \iota \pi 1 \drop \rho A  ] \nonumber \\
\times a[ (( \gamma(<1-i >; <1 \take (\rho A>))) \times \pi ( 1 \drop (\rho A))   )  + \iota \pi 1 \drop \rho A  ] 
\end{eqnarray}
Reducing, we get
\begin{eqnarray}
a[ (( \gamma(<2-i >; <3>))) \times \pi ( <5\;4>)  + \iota \pi <5\;4> ] \nonumber \\
\times a[ (( \gamma(<1-i >; <3>))) \times \pi ( <5\;4>)   )  + \iota \pi <5\;4>  ]\nonumber \\
a[( (2-i) \times  20)  + \iota 20 ] \nonumber \\
\times a[( (i-1) \times 20 )  + \iota 20 ]
\end{eqnarray}
\normalsize
Which breaks the indexing into start, stride, and stop, a universal hardware description and easiliy transformed
to the mnemonics used at any hardware level ~\cite{fftharry}.
We could add more dimensions to analyze prefetching, buffer sizes, vector registers, cache, etc.
